Linked Open Social Data for Scientific Benchmarking (Supporting Information document)

### 2016-08-01 paper.tex
some queries added and diagrams updated

\subsection{SPARQL queries}\label{queries}
There are numerous useful and general purpose SPARQL queries to be performed against the database.
Here we write some of the most basic of such queries selected by their potential to be varied.
All queries assume the use the preamble \textttt{PREFIX po: <http://purl.org/socialparticipation/po/>}.
\begin{enumerate}[leftmargin=0cm]
	\item Retrieve the number of participants:\\
            \textttt{SELECT (COUNT(DISTINCT ?author) as ?c) WHERE \{
            ?author a po:Participant . \} }
	\item Retrieve the number of relations, be them interactions or
            friendships:\\
            \textttt{SELECT (COUNT(?interaction) as ?c) WHERE \{\\
                    \h \{ ?interaction a po:Friendship \} UNION \{ ?interaction
                    a po:Interaction \} UNION\\
                    \h \{ ?interaction po:retweetOf
                    ?message \} UNION \{ ?interaction po:replyTo ?message
                    \}\\
                    \h UNION \{ ?interaction po:directedTo ?participant
                    \}\\ \} }
	\item Retrieve all text produced by an specific user:\\
            \textttt{SELECT (CONCAT(?text) as ?texts) WHERE \{\\
                    \h ?activity po:author <user\_uri> . ?activity po:text ?text .\\
    \}}
        \item List 1000 users (URIs and names) with the most friendships and the number of
            friendships in descending order by the number of friendships:\\
            \textttt{SELECT DISTINCT ?participant (COUNT(?interaction)
            as ?c) WHERE \{\\
                \h ?interaction a po:Friendship . ?interaction po:member ?participant . \\
            \} ORDER BY DESC(?c) LIMIT 1000}
	\item Search string ``pineapple'' in LOSD messages:\\
            \textttt{SELECT ?text WHERE \{ \\
                    \h ?activity po:text ?text . FILTER regex(?text, 'pineapple', 'i')\\
    \}}
\end{enumerate}

>>>>

\subsection{SPARQL queries}\label{queries}
There are numerous useful and general purpose SPARQL queries to be performed against the database.
Here we write some of the most basic of such queries selected by their potential to be varied.
All queries assume the use the preamble \textttt{PREFIX po: <http://purl.org/socialparticipation/po/>}.
\begin{enumerate}[leftmargin=0cm]
	\item Retrieve the number of participants:\\
            \textttt{SELECT (COUNT(DISTINCT ?author) as ?c) WHERE \{
            ?author a po:Participant . \} }
	\item Retrieve the number of relations, be them interactions or
            friendships:\\
            \textttt{SELECT (COUNT(?interaction) as ?c) WHERE \{\\
                    \h \{ ?interaction a po:Friendship \} UNION \{ ?interaction
                    a po:Interaction \} UNION\\
                    \h \{ ?interaction po:retweetOf
                    ?message \} UNION \{ ?interaction po:replyTo ?message
                    \}\\
                    \h UNION \{ ?interaction po:directedTo ?participant
                    \}\\ \} }
	\item Retrieve all text produced by an specific user:\\
            \textttt{SELECT (CONCAT(?text) as ?texts) WHERE \{\\
                    \h ?activity po:author <user\_uri> . ?activity po:text ?text .\\
    \}}
        \item List 1000 users (URIs and names) with the most friendships and the number of
            friendships in descending order by the number of friendships:\\
            \textttt{SELECT DISTINCT ?participant (COUNT(?friendship)
            as ?c) WHERE \{\\
                \h ?friendship a po:Friendship . ?friendship po:member ?participant . \\
            \} ORDER BY DESC(?c) LIMIT 1000}
        \item Retrieve text messages with the word ``pineapple'' (case insensitive):\\
            \textttt{SELECT ?text WHERE \{ \\
                    \h ?activity po:text ?text . FILTER regex(?text, 'pineapple', 'i')\\
    \}}
\item List participants and respective full names whose name has the substring ``Amanda'':\\
    \textttt{SELECT DISTINCT ?participant ?name WHERE \{\\
    \h ?participant po:observation ?obs . ?obs po:name ?name .\\
    \h FILTER regex(?name, 'Amanda', 'i') \\
    \}}
\item Return all pairs of friends of a participant which are friends themselves:\\
    \textttt{SELECT DISTINCT ?friend1 ?friend2 WHERE \{\\
     \h       ?friendship1 po:member <participant\_uri> .  ?friendship1 po:member ?friend1 .\\
     \h       ?friendship2 po:member <participant\_uri> .  ?friendship2 po:member ?friend2 .\\
     \h       ?friendship3 po:member ?friend1 .  ?friendship3 po:member ?friend2 .\\
    \}}
\item Return all interactions from replies in a snapshot:\\
    \textttt{SELECT ?from ?to WHERE \{\\
          \h  ?message1 po:snapshot <snapshot\_uri> .  ?message2 po:replyTo ?message1 .\\
          \h  ?message1 po:author ?from .  ?message2 po:author ?to .\\
    \}}
\end{enumerate}

### 2016-08-01 supportingInformation.tex
some queries added and diagrams updated

\section{Email data}
Each email snapshot is yield by an Email list.
Interactions are yield through \textttt{po:replyTo} relations
although \textttt{po:to} and \textttt{po:cc} might also be considered.
The email body is given by \textttt{po:text} relations while
\textttt{po:cleanText} links to text with lines removed where they are
trivially from previous messages or computer code.
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.4]{ontologies/gmane-legacy-linux.audio.devel1-20000Email00000.ttl/draw.png}
\textheight = 3in
\pdfpageheight 6in
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.5]{ontologies/gmane-legacy-linux.audio.devel1-20000Meta.ttl/draw.png}

>>>>

\section{Email data}
Each email snapshot is yield by an Email list.
Interactions are yield through \textttt{po:replyTo} relations
although \textttt{po:to} and \textttt{po:cc} might also be considered.
The email body is given by \textttt{po:text} relations while
\textttt{po:cleanText} links to text with lines removed where they are
trivially from previous messages or computer code.
Further information is found on the following diagrams, the tables on
the end of this document or in the main document of this
article~\cite{losd}.
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.4]{ontologies/email-legacy-linux.audio.devel1-20000Email00000.ttl/draw.png}
\textheight = 3in
\pdfpageheight 6in
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.5]{ontologies/email-legacy-linux.audio.devel1-20000Meta.ttl/draw.png}
